---
title: "Create 2022 Data - Vacancy"
author: "Christopher Prener, Ph.D."
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: 
  github_document: default
  html_notebook: default 
---

## Introduction
This notebook creates the vacancy data for the Spring 2022 final projects.

## Dependencies
This notebook requires:

```{r load-packages, message = FALSE}
# tidyverse packages
library(dplyr)
library(readr)

# other packages
library(here)
```

## Raw Data
This notebook requires data that can be automatically downloaded from the [Vacancy Collaborative's](https://www.stlvacancytools.com) open data portal:

```{r download-data}
vacant <- read_csv("https://www.publicgoodness.org/stlv/csv/stl_vacancy_data.csv",
                   col_types = cols(Handle = col_character()))
```

## Subset
There are some variables that we'll get rid of before exporting the data:

```{r subset-cols}
vacant %>% 
  select(-c("Ward20", "Ward10", "NhdName", "CensTract20", "CensTract10")) %>%
  relocate(Lat, Lng, .after = last_col()) -> vacant
```

## Write Data
Finally, we'll write the data to `.csv`:

```{r write-data}
write_csv(vacant, here("data", "vacant.csv"))
```
